\section{Questionnaire findings}
The group has found, from the 19 responses, that in general about 4 different personas can be found, moreover two further personas exist in different branches. These personas have been separated by whether or not they have actively tried to enhance their own personal security, and their evaluation of how much they feel their privacy is preserved "versus" gut feel on how much information they think is available about them self. Some of the participants have filled in their contact information and confirmed their willingness of participation in follow-up interviews.

\subsection{Persona 1 (The non concerned):}
This is the most common persona, with about 8 of the results.
This persona mostly uses their computer for personal matters or entertainment, are active at 7-8 different social media a day,
and uses their home computer for an average of 6 - 8 hours a day.
They are not concerned what others think of them, and therefore also do not hide their personality on social media.
They feel, to a greater extent, than the other personas, that their privacy is preserved on the internet, though they still know that most of their information is publicly available.
They have searched their own name online, mostly for fun, but really do not care about actively trying to enhance their privacy with use of VPN or the like.\\

\textit{From this Persona exists two branches:}
\begin{itemize}
    \item 
    \textbf{The Knowing:}\\
    This branch is highly aware that all of their personal information is publicly available, mainly because of their extensive use of social media.
    \item 
    \textbf{The Ignorant:}\\
    This branch knows that their personal information is public available, though they still believe that some information would be hard, or impossible, to find on the internet.
\end{itemize}

\subsection{Persona 2 (The concerned):}
This is the second most common persona, with about 6 participants fitting the description.
This persona mostly uses their computer for entertainment or work, is active at 6-7 different social media a day,
and uses their devices for an average of 8-10 hours a day.
They are, in some way, concerned what others think of them, and therefore also, to some extend, try to act a certain way on social media, to seem nice and polite.
They feel, to a lesser extend, that their privacy is not preserved on the internet, and here the two branches also differ the most.
They have searched their own name online, and care about trying to enhance their privacy with use of VPN or the like.\\

\textit{From this Persona exists two highly different branches:}
\begin{itemize}
    \item 
    \textbf{The Successful:}\\
    This branch do not feel that their privacy is preserved, and thereby also actively try to enhance their security. They also feel pretty successful in their endeavour, or is rather ignorant of their failure.
    \item 
    \textbf{The Failed:}\\
    This branch do neither feel that their privacy is preserved, despite their high curiosity, nor do they feel that they have succeeded in their security attempts.
\end{itemize}

\subsection{Persona 3 (The user)}
This persona can not really be classified to a single use, as they use there computer the the sake off nessarity, there ever its for school, work or sical matters they only use there computer cause its necessarily, also they can be active in any average of time and sicail media a day.
They do not act differently at media or real life as they don't know see the diffrence.
They do not necessarily feel that there privacy is perserved at the internet, and both due this there aspect off use they dount try to enhance ther privacy in any way.
They could have tried searching there name, but either way they really do not know in that extent there information is public aviable.

\subsection{Persona 4 (The Extremus)}
This persona either cant fit another perona due there extreamly confligting responses, Totaly fit a persona to perfection but so extreamly that is over the top, or have in some modified there results to a suspicious extent.