\section{Questionnaire methods and execution}
\noindent
This survey [View in appendix \ref{appendix:survey}] intends to explore the level of user awareness regarding privacy. \\
Firstly, it will be determined to which extent the individual user utilizes the internet.\\ 
Secondly, the type of user is determined. \\
Thirdly, the user is asked about their view on their personal privacy on the internet.\\
This is done to explore the possible correlation between amount of use, type of use and privacy view. \\
This information is intended to shed light on whether or not different user groups are likely to use a product capable of enhancing the security of their personal information and freedom on the internet.\\\\
\noindent
The questions in the survey were done in such a way as to allow for classification of the participants.
The survey also asked for permission to conduct follow-up interviews. These interviews intended to provide deeper insight into the reasoning behind certain behaviors. The individuals interviewed would bear close resemblance to one of the personas created to further enhance the insight into these personas.\\\\
\noindent
The intent of the survey was to clarify the archetypes of possible users to allow for the creation of a number of personas. These personas would then be used to create the relevant requirements for the product.
\noindent
Given that the participants have all been present at the university, studying some form of engineering, one possible error is that these participants might have a higher than average technical skill level as well as higher awareness of internet privacy issues.